TAR System Description Paper Template

### 2017-05-25 paper/paper.tex
Improved Cacher, added dummy Cacher factory method, implemented predict in PipelineAuthorDiarizer
Added SimpleGroupRepelTransformer

\title{Template for writing TAR project papers}

@@

\abstract{ 
This document provides the instructions on formatting the TAR project paper in \LaTeX{}. This is where you write the abstract (i.e., summary) of the work you carried out. The abstract is a paragraph of text ranging between 70 and 150 words.
}

@@

This section is the introduction to your paper. Introduction should not be too elaborate, that is what other sections are for (the Introduction should definitely not spill over to the second page).

@@

In scientific papers, this section usually (but not necessarily) briefly describes the related research.

@@

This is the second subsection of the second section. Referencing the (sub)sections in text is performed as follows: ``in Section \ref{sec:first} we have shown \dots''.

@@

The paper should have a minimum of 3 and a maximum of 5 pages, plus an additional page for references.

@@

Table~\ref{tab:narrow-table} is an example of a narrow table. Do not use vertical lines in tables -- vertical tables have no effect and they make tables visually less attractive.

@@

\[
b^{(i)}_k = \begin{cases}
1 & \text{if 
    $k = \text{argmin}_j \| \mathbf{x}^{(i)} - \mathbf{\mu}_j \|$}\\
0 & \text{otherwise}
\end{cases}
\]

>>>>

\title{TAR System Description Paper Template}

@@

\abstract{ 
This document provides the instructions on formatting the TAR system description paper in \LaTeX{}. This is where you write the abstract (i.e., summary) of the work you carried out within the project. The abstract is a paragraph of text ranging between 70 and 150 words.
}

@@

This section is the introduction to your paper. Introduction should not be too elaborate, as that is what other sections are for (the Introduction should definitely not spill over to the second page).

@@

In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.

@@

This is the second subsection of the second section. Referencing the (sub)sections in text is performed as follows: ``in Section~\ref{sec:first} we have shown \dots''.

@@

The paper should have a minimum of 3 and a maximum of 4 pages, plus an additional page for references.

@@

Table~\ref{tab:narrow-table} is an example of a narrow table. Do not use vertical lines in tables -- vertical tables have no effect and they make tables visually less attractive. We recommend using \textit{booktabs} package for nicer tables.

@@

\[
b^{(i)}_k = \begin{cases}
1 & \text{if 
    $k = \text{argmin}_j \| \mathbf{x}^{(i)} - \mathbf{\mu}_j \|,$}\\
0 & \text{otherwise}
\end{cases}
\]
